\sysfull

### 2018-04-16 paper/evaluation.tex
minor changes

%\begin{wrapfigure}{t!}{0.5\textwidth}
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalStrategies}
	\caption{\sys coalescing strategies performance per application on intermittent power (RF generator at 15\,cm from the WISP) compared to \sys without coalescing. \sys task coalescing strategy provides significant improvements (from 0.25, \textbf{ar}, up to 0.70, \textbf{sort}) compared to a non-coalesced system. \todo{no coalescing missing; change names of algos; reduce Y width by 40\%; names of apps bold and capitalized}{Przemek}}
	\label{fig:coalescing}
\end{figure}
%\end{wrapfigure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coala_alpaca_gcc}
	\caption{Performance of \sys applications at multiple WISP to RF generator antenna distances \{0.15, 0.3, 0.5\}\,m (left, center and right-most bar per application, respectively), compared against Alpaca (results normalized). Results show that \sys performs on average better than Alpaca for majority of the benchmarks. For specific benchmarks \sys performs worse than Alpaca \todo{state why it is sometimes worse}{Przemek} \todo{Add non-coalescing result; names of apps bold; reduce Y axis by 40\%; tiny spaces in-between bars for the same app}{Amjad}}
	\label{fig:runtime}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/overallOverhead}
	\caption{Overall \sys overhead breakdown; NC: no coalescing, SC: slow coalescing, EA: energy-aware coalescing. \todo{names of coalescing strategies in capitals; names of apps bold; reduce figure size by 40\%; app -> application; \& -> and; overall overhead breakdown -> overhead breakdown}{Amjad}}
	\label{fig:overallOverheadBreakdown}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalEfficiency}
	\caption{\sys coalescing algorithm efficiency; NC: no coalescing, SC: slow coalescing, EA: energy-aware coalescing, ETA: energy and task-aware coalescing. \todo{names of coalescing strategies in capitals; names of apps bold; reduce figure size by 40\%; app -> application; \& -> and;  colaescing algorithm efficiency -> overhead breakdown}{Amjad}}
	\label{fig:coalEfficiency}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/page_exec-time}
	\includegraphics[width=\columnwidth]{figures/pagePulls}
	\caption{\sys normalized runtime for various page sizes, \{32, 64,128,256\}\,bytes, per application (top) and respective page pulls (bottom)).\todo{add page numbers below for each bar for page faults; \# -> No. page faults; app names in bold; reduce Y size by 40\%; small space after 128 and 256 in top graph; white background}{Amjad}}
	\label{fig:page_size}
\end{figure}

>>>>

\begin{wrapfigure}{t!}{0.5\textwidth}
%\begin{figure}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/coalStrategies}
	\caption{\sys coalescing strategies performance per application on intermittent power (RF generator at 15\,cm from the WISP) compared to \sys without coalescing. \sys task coalescing strategy provides significant improvements (from 0.25, \textbf{ar}, up to 0.70, \textbf{sort}) compared to a non-coalesced system.}
	\label{fig:coalescing}
%\end{figure}
\end{wrapfigure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coala_alpaca_gcc}
	\caption{Performance of \sys applications at multiple WISP to RF generator antenna distances \{0.15, 0.3, 0.5\}\,m (left, center and right-most bar per application, respectively), compared against Alpaca (results normalized). Results show that \sys performs on average better than Alpaca for majority of the benchmarks. For specific benchmarks \sys performs worse than Alpaca \todo{state why it is sometimes worse}{Przemek}}
	\label{fig:runtime}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/overallOverhead}
	\caption{Overall \sys overhead breakdown; NC: no coalescing, SC: slow coalescing, EA: energy-aware coalescing.}
	\label{fig:overallOverheadBreakdown}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coalEfficiency}
	\caption{\sys coalescing algorithm efficiency; NC: no coalescing, SC: slow coalescing, EA: energy-aware coalescing, ETA: energy and task-aware coalescing.}
	\label{fig:coalEfficiency}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.49\columnwidth]{figures/page_exec-time}
	\includegraphics[width=0.49\columnwidth]{figures/pagePulls}
	\caption{\sys normalized runtime for various page sizes, \{32, 64,128,256\}\,bytes, per application (top) and respective page pulls (bottom)).\todo{add page numbers below for each bar for page faults; \# -> No. page faults; app names in bold; reduce Y size by 40\%; small space after 128 and 256 in top graph; white background}{Amjad}}
	\label{fig:page_size}
\end{figure}
